---
title: "Practical Machine Learning Peer-graded assignment"
author: "Dhruva Agrawal"
date: "10/25/2019"
output: html_document
---
##Introduction

With the advent and use of devices such as Jawbone Up, Nike FuelBand and Fitbit, it has now become possible to collect obscenely large amounts of data about a person's personal activity.
In this submission, this has been put to use as data from accelerometers on the belt, forearm and dumbbell of 6 participants were quantified and a prediction on this quantified data was made.

##Libraries and Dataset

```{r}
library(caret)
library(rpart)
library(rpart.plot)
library(RColorBrewer)
library(RGtk2)
library(rattle)
library(randomForest)
```
```{r}
UrlTrain <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
UrlTest  <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

# download the datasets
dt_training <- read.csv(url(UrlTrain))
dt_testing  <- read.csv(url(UrlTest))
```

##Cleaning the data

```{r}
features <- names(dt_testing[,colSums(is.na(dt_testing)) == 0])[8:59]

# Only use features used in testing cases.
dt_training <- dt_training[,c(features,"classe")]
dt_testing <- dt_testing[,c(features,"problem_id")]

dim(dt_training); dim(dt_testing);
```

##Partioning the dataset

```{r}
set.seed(12345)

inTrain <- createDataPartition(dt_training$classe, p=0.6, list=FALSE)
training <- dt_training[inTrain,]
testing <- dt_training[-inTrain,]

dim(training)
```
```{r}
dim(testing)
```

##Building the Decision Tree model

```{r}
modFitDT <- rpart(classe ~ ., data = training, method="class")
fancyRpartPlot(modFitDT)
```

##Making a prediction with the Decision Tree model

```{r}
set.seed(12345)

prediction <- predict(modFitDT, testing, type = "class")
confusionMatrix(prediction, testing$classe)
```

##Building the Random Forest model

```{r}
set.seed(12345)
modFitRF <- randomForest(classe ~ ., data = training, ntree = 1000)
```

##Making a prediction with the Random Forest model

```{r}
prediction <- predict(modFitRF, testing, type = "class")
confusionMatrix(prediction, testing$classe)
```

##Predicting on the Testing Data 

```{r}
predictionDT <- predict(modFitDT, dt_testing, type = "class")
predictionDT
```

##Random Forest Prediction

```{r}
predictionRF <- predict(modFitRF, dt_testing, type = "class")
predictionRF
```

##Analysis - As can be seen, Random Forest model is very accuracte, with almost 99% accuracy. 

##Preparing the Submission
```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(predictionRF)
```